\begin{thebibliography}{9}

\bibitem{horse}
  Inria (2004). \emph{A horse model}. This is a typical example model for LSCM
  parameterization algorithm.  Aim@Shape Project - Shape Repository.
  Available at:
  \url{http://shapes.aim-at-shape.net/view.php?id=31}

\bibitem{shading-source}
  \href{http://www.flickr.com/photos/manuela_w/}{Manuela W1}.  \emph{Values:
  Different types of shading} used under
  \href{http://creativecommons.org/licenses/by-nc-sa/2.0/}{(CC BY-NC-SA 2.0)}
  license.  Available at:
  \url{http://www.flickr.com/photos/manuela_w/5063203636}

\bibitem{hatching-source}
  \href{http://www.flickr.com/photos/manuela_w/}{Manuela W1}.  \emph{Example:
  cross hatch} used under
  \href{http://creativecommons.org/licenses/by-nc-sa/2.0/}{(CC BY-NC-SA 2.0)}
  license.  Available at:
  \url{http://www.flickr.com/photos/manuela_w/5063203640}

\bibitem{curvature-study}
  Timothy D. Gatzke and Cindy M. Grimm (2006). \emph{Estimating Curvature on
  Triangular Meshes}.  Available at:
  \url{http://www.worldscinet.com/ijsm/mkt/free/S0218654306000810.pdf}

\bibitem{taubin}
  Gabriel Taubin (1995). \emph{Estimating the Tensor of Curvature of a Surface
  From a Polyhedral Approximation}.  Available at:
  \url{http://mesh.caltech.edu/taubin/publications/taubin-iccv95b.pdf}

\bibitem{principal-curvature-source}
  \href{http://commons.wikimedia.org/wiki/User:Sting}{Eric Gaba (Sting)}.
  \emph{View of the planes establishing the main curvatures on a minimal
  surface} used under \href{http://creativecommons.org/licenses/by-sa/2.0/}{(CC
  BY-SA 2.0)} license.  Available at:
  \url{http://en.wikipedia.org/wiki/File:Minimal_surface_curvature_planes-en.svg}

\end{thebibliography}
